Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-02 paper/main.tex
S,K, I

\subsection{Continuity}
\label{sec:related-work:continuity}
\begin{figure}[!h]
  \includegraphics[width=\columnwidth]{k_different_types.png}
  \caption{Continuity is how elements in a data set are connected to each other, which is distinct from how the data is structured. The rows in (a) are discrete, therefore they have discrete continuity as illustrated by the discrete dots. The gaussian in (b) is a 1D continuous function, therefore the continuity of the elements of the gaussian can be represented as a line on an interval (0,1). In (c), every element of the globe is connected to its nearest neighbors, which yields a 2D continuous continuity as illustrated by the square.}
  \label{fig:related-work:continuity}
\end{figure}
Continuity describes elements in a data set are organized; this concept is termed topological properties by Wilkinson\cite{wilkinsonGrammarGraphics2005}. Wilkinson provides the examples of values that are isolated from each other, and therefore discrete, and values lying on a continuum or in a compact region. For example, in \autoref{fig:related-work:continuity}, each station record in the table is independent of the others; therefore, the continuity of the table is discrete. The data provided by the gaussian are points sampled along the curve, therefore the continuity of the points on the line is 1D continuous. Every point on the globe is connected to its 6 nearest cardinal neighboring points (NW, N, NE, E, SE, S, SW, W). We propose that a robust model of continuity provides a way to develop library components that can work on the data in small pieces in a manner where the overall continuity of the data is preserved in the visual transformation.

\begin{figure}[!h]
  \includegraphics[width=\columnwidth]{whycontinuity.png}
  \caption{Continuity is implicit in choice of visualization rather than explicitly in choice of data container. The line plots in (b) are generated by a 2D table (a). Structurally this table can be identical to the 2D matrix (a) that generates the image in (c).}
  \label{fig:related-work:visual-algorithm}
\end{figure}

@@

\begin{figure}[!h]
  \label{fig:related-work:equivariance}
  \includegraphics[width=\columnwidth]{equiv.png}
  \caption{Equivariance is that a transformation on the data has a corresponding transformation in the graphical representation. For example, in this figure the data is scaled by a factor 10. Equivalently the line plot is scaled by factor of 10, resulting in a shrunken line plot. Either a transformation on the data side can induce a transformation on the visual side, or a transformation on the visual side indicates that there is also a transformation on the data side. }
\end{figure}

@@

We model a space of data sets with the same continuity and fields as the sheaf  $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op} \textcolor{sheaf}{\rightarrow} \setc$.
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc}{\dtotalc|_{\opensetc}} \in Ob(\setc) & \\
    {} & & {} \\
    & \opensetc \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \arrow[uu, "\sheafc(\dtotalc)"', shift left = 10, color=sheaf] &   
\end{tikzcd}
\end{equation}
The objects of \textbf{Set} in this sheaf are the sets of sections $\Gamma(\dbase, \dtotal)$ introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps $(\iota, \iota^*)$ introduced in \autoref{eq:related-work:continuity:presheaf}. As mentioned in \autoref{re} sections $\dsection$ are

\note{add transition sentence about artist }

The continuity of the graphic is encapsulated as a category $\mathcal{\gbase}}$

@@

\subsubsection{Shared Index}
\begin{figure}[!h]
  \includegraphics[width=\columnwidth]{k_union.png}
  \label{fig:artist:union:disjoint_k}
  \caption{In \autoref{fig:artist:union:k}, the input object $\sheaf_{\dtotal}$ encodes a continuous function over spaces $\dtotal_a$, $\dtotal_b$ 
  and overlapping space $\dtotal_c$. In this figure, the visual transformation is to a point on the line on screen. An artist that preserves the continuity of the function must generate graphics such that functions evaluated  $\dbasepoint \in \dbase_a \cap \dbase_b$}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \subfloat[\note{insert title}]{\includegraphics[width=1.2in]{partial_fixed.png}%
  \label{fig_first_case}}
  %\hfill
  \subfloat[\note{insert title}]{\includegraphics[width=1.2in]{partial_invalid.png}%
  \label{fig_second_case}}
  \caption{is a weird nu, colors are a but much}
  \label{fig_sim}
\end{figure}

\paragraph{Multiview Constraints}
\begin{figure}[!h]
  \centering
  \subfloat[No shared fields]]{\includegraphics[width=.4\columnwidth]{exploding_artist.png}%
  \label{fig:artist:union:k}}
  %\hfill
  \subfloat[Shared fields]{\includegraphics[width=.4\columnwidth]{combined_artist.png}%
  \label{fig:artist:union:disjoint_k}}
  \caption{In \autoref{fig:artist:union:k}, the input object $\sheaf_{\dtotal}$ encodes a continuous function over spaces $\dtotal_a$, $\dtotal_b$ 
  and overlapping space $\dtotal_c$. In this figure, the visual transformation is to a point on the line on screen. An artist that preserves the continuity of the function must generate graphics such that functions evaluted  $\dbasepoint \in \dbase_a \cap \dbase_b$
  \note{replace a) w/ fiber cross diagram? - use first half introduced in \autoref{fig:artist:compose:union_fiber}}}
\end{figure}

@@

\begin{figure}[!h]
  \includegraphics[width=\columnwidth]{diff_type_q.png}
  \caption{rework this as a commutative box w/ the r in E row associated w/ this qhat(k)}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \subfloat[\dbasec_a \sqcup_{\dbasec_c} \dbase_b]{\includegraphics[width=1.2in]{union_k.png}%
  \label{fig_first_case}}
  %\hfil
  \subfloat[\dbasec_c=\varnothing]{\includegraphics[width=1.2in]{disjoint_k.png}%
  \label{fig_second_case}}
  \caption{\note{probably doesn't need the k=0}}
  \label{fig_sim}
\end{figure}

>>>>

\subsection{Continuity}
\label{sec:related-work:continuity}
\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{k_different_types.png}
  \caption{Continuity is how elements in a data set are connected to each other, which is distinct from how the data is structured. The rows in (a) are discrete, therefore they have discrete continuity as illustrated by the discrete dots. The gaussian in (b) is a 1D continuous function, therefore the continuity of the elements of the gaussian can be represented as a line on an interval (0,1). In (c), every element of the globe is connected to its nearest neighbors, which yields a 2D continuous continuity as illustrated by the square.}
  \label{fig:related-work:continuity}
\end{figure}
Continuity describes elements in a data set are organized; this concept is termed topological properties by Wilkinson\cite{wilkinsonGrammarGraphics2005}. Wilkinson provides the examples of values that are isolated from each other, and therefore discrete, and values lying on a continuum or in a compact region. For example, in \autoref{fig:related-work:continuity}, each station record in the table is independent of the others; therefore, the continuity of the table is discrete. The data provided by the gaussian are points sampled along the curve, therefore the continuity of the points on the line is 1D continuous. Every point on the globe is connected to its 6 nearest cardinal neighboring points (NW, N, NE, E, SE, S, SW, W). We propose that a robust model of continuity provides a way to develop library components that can work on the data in small pieces in a manner where the overall continuity of the data is preserved in the visual transformation.

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{whycontinuity.png}
  \caption{Continuity is implicit in choice of visualization rather than explicitly in choice of data container. The line plots in (b) are generated by a 2D table (a). Structurally this table can be identical to the 2D matrix (a) that generates the image in (c).}
  \label{fig:related-work:visual-algorithm}
\end{figure}

@@

\begin{figure}[h!]
  \label{fig:related-work:equivariance}
  \includegraphics[width=\columnwidth]{equiv.png}
  \caption{Equivariance is that a transformation on the data has a corresponding transformation in the graphical representation. For example, in this figure the data is scaled by a factor 10. Equivalently the line plot is scaled by factor of 10, resulting in a shrunken line plot. Either a transformation on the data side can induce a transformation on the visual side, or a transformation on the visual side indicates that there is also a transformation on the data side. }
\end{figure}

@@

We model a space of data sets with the same continuity and fields as the sheaf  $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op} \textcolor{sheaf}{\rightarrow} \setc$.
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc}{\dtotalc|_{\opensetc}} \in Ob(\setc) & \\
    {} & & {} \\
    & \opensetc \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \arrow[uu, "\sheafc(\dtotalc)"', shift left = 10, color=sheaf] &   
\end{tikzcd}
\end{equation}
The objects of \textbf{Set} in this sheaf are the sets of sections $\Gamma(\dbase, \dtotal)$ introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps $(\iota, \iota^*)$ introduced in \autoref{eq:related-work:continuity:presheaf}.

An element of the sheaf, which is a section \dsection, is converted into a graphic. The topology of the graphic \gbase\ is determined both by the data continuity \dbase\ and the dimensionality of the display space 
\begin{equation}
  \gbase = \dbase \times I^{\text{dim}(display)-\text{dim}(\dbase)} 
\end{equation}
where $I$ is an arbitrary 1 dimensional interval. 
\begin{figure}[h!]
  \label{fig:artist:gbase}
  \includegraphics{scatter_s.png}
  \caption{The topology of the data, which is a 0 dimensional point, is expanded to a region in the 2D screen display space. It is expanded via the intervals $I_1, I_2$ such that all coordinates on the disk map back to the same K \note{maybe also include line example,or just use line example}}
\end{figure}
As illustrated in \autoref{fig:artist:gbase}, the interval $I$ is used to increase the dimensionality of the data topology \dbase, by padding it with intervals, such that it is compatible with the display space.

@@

\subsubsection{Shared Index}
\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{k_union.png}
  \label{fig:artist:union:disjoint_k}
  \caption{In \autoref{fig:artist:union:k}, the input object $\sheaf_{\dtotal}$ encodes a continuous function over spaces $\dtotal_a$, $\dtotal_b$ 
  and overlapping space $\dtotal_c$. In this figure, the visual transformation is to a point on the line on screen. An artist that preserves the continuity of the function must generate graphics such that functions evaluated  $\dbasepoint \in \dbase_a \cap \dbase_b$}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \subfloat[\note{insert title}]{\includegraphics[width=1.2in]{partial_fixed.png}%
  \label{fig_first_case}}
  %\hfill
  \subfloat[\note{insert title}]{\includegraphics[width=1.2in]{partial_invalid.png}%
  \label{fig_second_case}}
  \caption{is a weird nu, colors are a but much}
  \label{fig_sim}
\end{figure}

\paragraph{Multiview Constraints}
\begin{figure}[h!]
  \centering
  \subfloat[No shared fields]]{\includegraphics[width=.4\columnwidth]{exploding_artist.png}%
  \label{fig:artist:union:k}}
  %\hfill
  \subfloat[Shared fields]{\includegraphics[width=.4\columnwidth]{combined_artist.png}%
  \label{fig:artist:union:disjoint_k}}
  \caption{In \autoref{fig:artist:union:k}, the input object $\sheaf_{\dtotal}$ encodes a continuous function over spaces $\dtotal_a$, $\dtotal_b$ 
  and overlapping space $\dtotal_c$. In this figure, the visual transformation is to a point on the line on screen. An artist that preserves the continuity of the function must generate graphics such that functions evaluted  $\dbasepoint \in \dbase_a \cap \dbase_b$
  \note{replace a) w/ fiber cross diagram? - use first half introduced in \autoref{fig:artist:compose:union_fiber}}}
\end{figure}

@@

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{diff_type_q.png}
  \caption{rework this as a commutative box w/ the r in E row associated w/ this qhat(k)}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \subfloat[\dbasec_a \sqcup_{\dbasec_c} \dbase_b]{\includegraphics[width=1.2in]{union_k.png}%
  \label{fig_first_case}}
  %\hfil
  \subfloat[\dbasec_c=\varnothing]{\includegraphics[width=1.2in]{disjoint_k.png}%
  \label{fig_second_case}}
  \caption{\note{probably doesn't need the k=0}}
  \label{fig_sim}
\end{figure}
